---
title: "Analysis"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(maps)         # for state maps
#devtools::install_github("hrbrmstr/hrbrthemes") 
```

```{r df_tidy, collapse=TRUE,message=FALSE, include=FALSE}
tax_df = read_csv( "data_import_cleaning/tax.csv")
state_tax_df = read_csv("data_import_cleaning/state_tax_df.csv")

# https://abbreviations.yourdictionary.com/articles/state-abbrev.html
state_ref = 
  read.delim("./data_import_cleaning/state_abbreviation.txt", header = F) %>%
  separate(V1, into = c("state", "state_abbrv"), sep = " - ") 

# jurisdiction information
license = 
  read_table("./data_import_cleaning/license_jurisdiction_modified.txt") %>%
  unlist()
control = 
  read_table("./data_import_cleaning/control_jurisdiction_modified.txt") %>%
  unlist()

# tidy tax data: state with abbreviation + group
# to be consistent with other plots, remove year 2008, 2009 (starting year is 2010)
tax_df_group =  
  left_join(tax_df %>% rename(state_abbrv = state), 
            state_ref, by = "state_abbrv") %>% 
  mutate(
    group = ifelse(state %in% license, "licensed", 
                   ifelse(state %in% control, "control", "NA"))
  ) %>% 
  relocate(state_abbrv, state, group) %>% 
  slice(-52) %>% 
  select(-`2008`, -`2009`)

state_tax_df_group = 
  left_join(state_tax_df, state_ref, by = "state") %>% 
  mutate(
    group = ifelse(state %in% license, "licensed", 
                   ifelse(state %in% control, "control", "NA"))
  ) %>% 
  relocate(state_abbrv, state, group) %>% 
  filter(year != "2009")
```

We focus on two analyses in this section. One is to compare tax differences by jurisdiction group over time. The other is to model taxation under the regression analysis framework. 

---

# Preliminary Analysis 

$~$

## Goal

**To Compare Tax differences by jurisdiction group** 

Differing on the degree of control on liquor wholesales and retail, states can be categorized into two [types](https://www.ncsla.org/State-Officials.html) -- control jurisdiction and licensed jurisdiction, with licensed states having more control. Such categorization may lead to difference in taxation. Therefore, we are interested in examining if there is any difference in taxation by these two groups of states. 

For viewing convenience, we display a state map showing the control jurisdiction and the licensed jurisdiction. 

```{r state_map, collapse=T, message=F}
us_states <- map_data("state")

states_map = 
  us_states %>% 
  mutate(
    state_group = 
      ifelse(region %in% str_to_lower(license), "licensed", 
             ifelse(region %in% str_to_lower(control), "control", "NA"))
  )

theme_map <- function(base_size = 9, base_family = "") {
    require(grid)
    theme_bw(base_size = base_size, base_family = base_family) %+replace%
        theme(axis.line = element_blank(),
              axis.text = element_blank(),
              axis.ticks = element_blank(),
              axis.title = element_blank(),
              panel.background = element_blank(),
              panel.border = element_blank(),
              panel.grid = element_blank(),
              panel.spacing = unit(0, "lines"),
              plot.background = element_blank(),
              legend.justification = c(0,0),
              legend.position = c(0,0)
              )
}
p0 <- ggplot(data = states_map,
             mapping = aes(x = long, y = lat,
                           group = group, fill = state_group)) +
  scale_fill_manual(values = c("snow3", "steelblue"))
p1 <- p0 + geom_polygon(color = "gray90", size = 0.1) +
    coord_map(projection = "albers", lat0 = 39, lat1 = 45) 
p2 <- p1 +
    labs(title = "Jurisdiction Group", fill = NULL)
p3 <- p2 + theme_map()

centroids <- data.frame(region = tolower(state.name), 
                        long = state.center$x, lat = state.center$y)
centroids$abb <- state.abb[match(centroids$region, tolower(state.name))]

# Collect names of the 32 states in my data.
statenames <- data.frame(region = unique(states_map$region)) 
# Merge it with centroids
centroids <- merge(statenames, centroids, by = "region")

p3 + 
  with(centroids, 
       annotate(geom = "text", x = long, y = lat, label = abb, 
                size = 2.3, color = "gray30")
      )
```

$~$ 

## Cumulative Tax Collected

First, we looked at the cumulative taxes collected. 
This tax is specifically looking at the “Beer removed for consumption or sale including beer removed tax determined for consumption or sale in a tavern or on brewery premises”. 

We performed t-test for each year and would like to see if the cumulative taxes collected differ significantly between the control states and the licensed states. 

The following plot gives the average tax difference (Tax in the Control States - Tax in the Licensed States), together with its 95% confidence interval and p-value, from 2010 to 2019. 

We can see that the mean difference in the cumulative tax collected does not deviate much from 0 for all years, though the confidence interval seems to have a fan shape over time. Large p-values from t-tests also suggest that there is **no sufficient evidence showing any significant difference between two jurisdiction groups in the cumulative tax collected from 2010 to 2019**.

```{r tax_group}
# tax
year = colnames(tax_df_group)[-c(1:3)]
t_test_output = NULL
for (i in 1:length(year)) {
  t_test = t.test(tax_df_group[[year[i]]]~group, data = tax_df_group) %>% broom::tidy()
  t_test_output = rbind(t_test_output, t_test)
}

tax_group_result = 
  t_test_output %>% 
  mutate(year = year) %>% 
  relocate(year) %>% 
  rename(
    control_est = estimate1, 
    licensed_est = estimate2, 
    control_minus_licensed = estimate) %>% 
  select(year, control_minus_licensed, p.value, conf.low, conf.high) %>% 
  janitor::clean_names() %>% 
  mutate(
    control_minus_licensed = control_minus_licensed / 1000,
    conf_low = conf_low / 1000, 
    conf_high = conf_high / 1000) %>% 
  mutate_at(2:3, round, 2)

tax_group_result %>% 
  mutate(year = as.character(year)) %>% 
  ggplot(aes(x = year, y = control_minus_licensed)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  labs(
    title = "Difference in Cumulative Tax between Control and Licensed Groups over time",
    subtitle = "Tax difference in orange; p-value in parentheses",
    y = "Tax Difference (Control - Licensed) (in thousand $)", 
    x = "Year") + 
  geom_text(
    aes(label = paste0("(", p_value, ")")), 
    color = "steelblue", hjust = -0.05, vjust = -3.7, angle = 20) + 
  geom_text(
    aes(label = control_minus_licensed), 
    color = "#D14124", hjust = 0.6, vjust = 1.5, angle = 20)
```

$~$ 

## Tax per Barrel

Next, we looked at the tax per barrel, which is the effective excise tax (volume adjusted). Similar to what have been done in previous subsection, we performed t-test for each year and would like to see if there is any significant difference in the tax per barrel between the control states and the licensed states. 

The following plot gives the average tax difference (Tax in the Control States - Tax in the Licensed States), together with its 95% confidence interval and p-value, from 2010 to 2019. 

We can see that the mean difference in the tax per barrel does not deviate much from 0 for all years, and the confidence interval seems to be consistently wide over time. Large p-values from t-tests again suggest that there is **no sufficient evidence showing any significant difference between two jurisdiction groups in the tax per barrel from 2010 to 2019**.

```{r state_tax_group}
# state_tax

state_tax_group_result = 
  state_tax_df_group %>% 
  nest(data = -year) %>% 
  mutate(
    t_test = purrr::map(.x = data, ~t.test(adjusted ~ group, data = .x)),
    result = purrr::map(t_test, broom::tidy)
  ) %>% 
  select(year, result) %>% 
  unnest(result) %>% 
  rename(control_est = estimate1, 
         licensed_est = estimate2,
         control_minus_licensed = estimate) %>% 
  select(year, control_minus_licensed, p.value, conf.low, conf.high) %>% 
  janitor::clean_names() %>% 
  mutate_at(2:3, round, 2)

state_tax_group_result %>% 
  mutate(year = as.character(year)) %>% 
  ggplot(aes(x = year, y = control_minus_licensed)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  labs(
    title = "Difference in Tax per Barrel between Control and Licensed Groups over time",
    subtitle = "Tax difference in orange; p-value in parentheses",
    y = "Tax Difference (Control - Licensed) in $",
    x = "Year") + 
  geom_text(
    aes(label = paste0("(", p_value, ")")), 
    color = "steelblue", hjust = -0.05, vjust = -3.5, angle = 20) +
  geom_text(
    aes(label = control_minus_licensed), 
    color = "#D14124", hjust = 0.6, vjust = 2, angle = 20)
```

$~$

## Recap

* **Cumulative tax collected** does **not differ significantly by jurisdiction groups** from 2010 to 2019. 
* **Tax per barrel** does **not differ significantly by jurisdiction groups** from 2010 to 2019. 


--- 

  
# Regression Anlaysis
  
In this part, we would like to explore more regarding the relationship between taxation and jurisdiction group, year, shipments, population, and consumption. To be consistent with our focus in the previous section, we fit two regression models -- one for the cumulative tax collected and the other for the tax per barrel.  

$~$

## Variables

Our explaining variables of interest include jurisdiction group, year, shipments, population, and consumption. 

* group: jurisdiction group (control vs licensed)
* shipments: amount of barrels shipped
* population: the number of individuals who are 21 years old or older
* consumption: consumption of barrels per capital

$~$ 

## Model 1 - Cumulative Tax Collected

We first focus on the **cumulative tax collected**. Our model of interest is: 

$$Cumulative \ tax = \beta_0 + \beta_1 \ Group + \beta_2 Year + \beta_3 \ Shipments + \beta_4 \ Population+ \beta_5 \ Consumption.$$

$~$ 

### Results

Variables with significant p-value are highlighted in blue.

```{r reg_df,collapse=T}
# Load state_df
state_df = read_csv("data_import_cleaning/state_df.csv")

# Merge dataset
reg_df = 
  tax_df_group %>% 
  pivot_longer(
    "2010":"2019", 
    names_to = "year", 
    values_to = "total_tax"
  ) %>% 
  mutate(year = as.numeric(year)) %>% 
  left_join(., state_df, by = c("state", "year")) %>% 
  select(total_tax, group, year, shipments, population, consumption)

# Replace 0's with NA's
reg_df[reg_df == 0] <- NA

# Fit model
lm_model = lm(total_tax ~ group + year + shipments + population + consumption, data = reg_df)
summary(lm_model)

broom::tidy(lm_model) %>% 
  mutate_at(2:5, format, digits = 2, nsmall = 1) %>% 
  janitor::clean_names() %>% 
  rename(
    Variable = term,
    Coefficient = estimate, 
    `Standard Error` = std_error,
    `t-Statistic` = statistic, 
    `P-value` = p_value
  ) %>% 
  mutate(
    Variable = ifelse(Variable == "grouplicensed", "Licensed Group", Variable), 
    Variable = str_to_title(Variable)
  ) %>% 
  DT::datatable(., rownames = F, 
                options = list(pageLength = 10)) %>% 
  DT::formatStyle(
    columns = "P-value",
    background = DT::styleInterval(c(0.05),c("lightsteelblue","white")), 
    target = "row")
```

$~$

### Interpretation

* All variables in our model are **significant** at the 5% significance level. 
* Our model fit is acceptable with an adjusted $R^2 = 0.55$. 
* Previously, we did not find any significant difference in the cumulative tax between two jurisdiction groups. However, after controlling for year, shipments, population and consumption, we found that **licensed states** are estimated to have approximately **$7.6k less cumulative tax collected** than the control states.
* **Cumulative tax collected** is estimate to 
  * **increase approximately $7k per year**, holding the group, shipments, population and consumption unchanged. 
  * **increase approximately $1.2k for one unit increase in consumption per capital**, holding the group, year, shipments, and population unchanged. 
  * **increase approximately $14 for each 1k increase in population**, holding the group, year, shipments, and consumption unchanged. 
  * **decrease approximately $9.6 for each 1k increase in shipments**, holding the group, year, population, and consumption unchanged. 

$~$

## Model 2 - Tax Per Barrel

We next look at the **tax per barrel**. Our model of interest is

$$Tax \ per \ barrel = \beta_0 + \beta_1 \ Group + \beta_2 Year + \beta_3 \ Shipments + \beta_4 \ Population+ \beta_5 \ Consumption.$$

$~$

### Results

Variables with significant p-value are highlighted in blue.

```{r reg_df2,collapse=T}
# Load state_df
state_df = read_csv("data_import_cleaning/state_df.csv")

# Merge dataset
reg_df2 = 
  state_tax_df_group %>% 
  rename(adjusted_tax = adjusted) %>% 
  mutate(year = as.numeric(year)) %>% 
  left_join(., state_df, by = c("state", "year")) %>% 
  select(adjusted_tax, group, year, shipments, population, consumption)

# Replace 0's with NA's
reg_df2[reg_df2 == 0] <- NA

# Fit model
lm_model2 = lm(adjusted_tax ~ group + year + shipments + population + consumption, data = reg_df2)
summary(lm_model2)

broom::tidy(lm_model2) %>% 
  mutate_at(2:5, format, digits = 2, nsmall = 1) %>% 
  janitor::clean_names() %>% 
  rename(
    Variable = term,
    Coefficient = estimate, 
    `Standard Error` = std_error,
    `t-Statistic` = statistic, 
    `P-value` = p_value
  ) %>% 
  mutate(
    Variable = ifelse(Variable == "grouplicensed", "Licensed Group", Variable), 
    Variable = str_to_title(Variable)
  ) %>% 
  DT::datatable(., rownames = F, 
                options = list(pageLength = 10)) %>% 
  DT::formatStyle(
    columns = "P-value",
    background = DT::styleInterval(c(0.05),c("lightsteelblue","white")), 
    target = "row")
```

$~$

### Interpretation

* All variables in our model are **not significant** at the 5% significance level. 
* This model does not fit well as the adjusted $R^2$ is approximately 0.


--- 


# Highlights

* Our data suggested that **tax per barrel** does **not differ significantly by jurisdiction groups** from 2010 to 2019. 
* After controlling for year, amount of barrels shipped, population above 21 years old and consumption of barrels per capital, we found that **licensed states** are estimated to have **less cumulative tax collected** than the control states from 2010 to 2019. 
  * In addition, **Cumulative tax collected** is estimate to **increase** with **year, consumption per capital and population** but **decrease** with **shipments**.  

$~$

