---
title: "Consumption"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(flexdashboard)

state_df = read_csv("data_import_cleaning/state_df.csv")
beer = read_csv("./data_import_cleaning/beer.csv")
```

--- 

## Consumption
This graph shows data from the [Shipments of Malt Beverages and Per Capita Consumption by State](https://www.nbwa.org/sites/default/files/2003%20and%202019%20State%20data%20Per%20Capita%20Sheets_1.pdf) document. This consumption is by captiate and only considers individuals who are 21 years old or older. 
```{r warning=FALSE, message=FALSE}
state_df %>%
  filter(year > 2009) %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~consumption, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Consumption")
```

---

## Alcohol by volume (ABV) pattern

**Alcohol by volume (ABV)** is defined to be the volume percent of alcohol (ethanol) contained in a given volume of an alcoholic beverage. 
In our project, we are interested in exploring the pattern of ABV concerning the category/brewer/style of beer. 

### By category

First, we looked at the pattern of ABV by beer's category. 

* It seems that **Belgian and French Ale** has the **highest** average ABV while the **North American Lager** has the **lowest** average AVB. 
* The distribution of ABV of Belgian and French Ale is relatively bell-shaped while the other categories are skewed. 

```{r cat_abv,collapse=TRUE}
cat_abv = 
  beer %>% 
  replace_na(list(category = "NA", y = "unknown")) %>% 
  group_by(category) %>% 
  summarise(mean_abv = mean(alcohol_by_volume)) %>% 
  arrange(desc(mean_abv)) 
cat_abv

cat_abv %>% 
  mutate(category = fct_reorder(category, mean_abv)) %>% 
  plot_ly(x = ~category, y = ~mean_abv, 
          color = ~category, type = "bar", colors = "viridis") %>% 
  layout(title = "Average ABV by Beer Category",
         xaxis = list(title = "Beer Category",
                      zeroline = TRUE),
         yaxis = list(title = "Average ABV",
                      range = c(0, 7)))

beer %>% 
  mutate(category = fct_reorder(category, alcohol_by_volume)) %>% 
  plot_ly(y = ~alcohol_by_volume, 
          color = ~category, type = "box", colors = "viridis") %>% 
  layout(title = "Boxplot of ABV by Beer Category",
         xaxis = list(title = "Beer Category",
                      zeroline = TRUE),
         yaxis = list(title = "ABV",
                      range = c(0, 21)))
```

### By brewer

Next, we looked at the pattern of ABV by beer's brewer. 

As there are 823 brewers listed in our dataset, we will show the **top 20** that has the highest average ABV, rather than all of them. 

* **Mendocino Brewing - Ukiah**has the highest average ABV. 
* There are 424 brewers having average ABV value of 0. 

```{r brewer_abv,collapse=TRUE}
brewer_abv = 
  beer %>% 
  group_by(brewer) %>% 
  summarise(mean_abv = mean(alcohol_by_volume)) %>% 
  arrange(desc(mean_abv))
brewer_abv

#brewer_abv %>% filter(mean_abv == 0) #424

brewer_abv %>% 
  slice(1:20) %>% 
  mutate(brewer = fct_reorder(brewer, mean_abv)) %>%
  plot_ly(x = ~brewer, y = ~mean_abv, 
          color = ~brewer, type = "bar", colors = "viridis") %>%
  layout(title = "Average ABV by Beer Brewer",
         xaxis = list(title = "Beer Brewer",
                      zeroline = TRUE),
         yaxis = list(title = "Average ABV",
                      range = c(8, 10.8)))

top_20_brewer = brewer_abv %>% slice(1:20) %>% select(brewer) %>% unlist()
beer %>% 
  filter(brewer %in% top_20_brewer) %>% 
  mutate(brewer = fct_reorder(brewer, alcohol_by_volume)) %>% 
  plot_ly(y = ~alcohol_by_volume, 
          color = ~brewer, type = "box", colors = "viridis") %>% 
  layout(title = "Boxplot of ABV by Beer Brewer",
         xaxis = list(title = "ABV",
                      zeroline = TRUE),
         yaxis = list(title = "Average ABV"))
```

### By style

Finally, we looked at the pattern of ABV by beer's style. 

There are 62 styles listed in our dataset, and we will show the **top 20** that has the highest average ABV, as well as the **lowest 5**. 

* We can see that **Belgian-Style Quadrupel** has the higherst average ABV while both **Vienna-Style Lager** and **Specialty Honey Lager or Ale** has average ABV of 0. 

```{r style_abv,collapse=TRUE}
style_abv = 
  beer %>% 
  group_by(style) %>% 
  summarise(mean_abv = mean(alcohol_by_volume)) %>% 
  arrange(desc(mean_abv))
style_abv

style_abv %>% 
  slice(1:20) %>% 
  mutate(style = fct_reorder(style, mean_abv)) %>% 
  plot_ly(x = ~style, y = ~mean_abv, 
          color = ~style, type = "bar", colors = "viridis")  %>%
  layout(title = "Average ABV by Beer Style",
         xaxis = list(title = "Beer Style",
                      zeroline = TRUE),
         yaxis = list(title = "Average ABV",
                      range = c(5.5, 12)))

tail(style_abv) %>% 
  rename(Style = style, `Average ABV` = mean_abv) %>% 
  slice(-1) %>% 
  mutate_at(2, round, 2) %>% 
  knitr::kable(caption = "Styles with Lowest 5 Average AVB") %>% 
  kableExtra::kable_styling(., bootstrap_options = c("striped", "hover"),
                            full_width = F)

#style_abv %>% 
#  rename(Style = style, `Average ABV` = mean_abv) %>% 
#  mutate_at(2, round, 2) %>% 
#  DT::datatable(., rownames = F) 

top_20_style = style_abv %>% slice(1:20) %>% select(style) %>% unlist()
beer %>% 
  filter(style %in% top_20_style) %>% 
  mutate(style = fct_reorder(style, alcohol_by_volume)) %>% 
  plot_ly(y = ~alcohol_by_volume, 
          color = ~style, type = "box", colors = "viridis") %>% 
  layout(title = "Boxplot of ABV by Beer Style",
         xaxis = list(title = "ABV",
                      zeroline = TRUE),
         yaxis = list(title = "Average ABV"))
```


