---
title: "Consumption"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(flexdashboard)

state_df = read_csv("data_import_cleaning/state_df.csv")
beer = read_csv("./data_import_cleaning/beer.csv")

library(ggplot2)
library(broom)
library(plotly)
library(highcharter)
library(rworldmap)
library(gganimate)
library(transformr)
library(corrplot)
library(leaps)
library(kableExtra)

library(gifski)

library(usdata)
```


This page concentrates on data collected from the American Beer Distributors and the Beer API. Its goal of this page is to explore how the consumption of beer differs between each state. Please view the dashboard to get a better understanding of the consumption per capita over time and by the state as well as a view of our data! 

--- 

## Consumption per Capita 

This graph shows data from the Per Capita Consumption by each state from the years 2010-2019 in barrel units. The population considers only people who are of age to drink (21+ years). The colors represent the different regions of each state.


```{r warning=FALSE, message=FALSE, fig.width = 8, fig.height = 7, cache=TRUE}
# setting up the regions
region_name = tibble(state = state.name, state_region= state.region)

sm3 = state_df %>%
  filter(state != "District of Columbia") %>%
  filter(year > 2009) %>%
  left_join(., region_name)

static_plot<-ggplot(sm3,aes(rank_6,group=state,fill=state_region,color=state_region)) +
 geom_tile(aes(y = consumption/2,height = consumption, width = 0.9), alpha = 0.8, color = NA) +
 geom_text(aes(y = 0, label = paste(state, ' ')), vjust = 0.2, hjust = 1, size = 3) +
 geom_text(aes(y = consumption, label = paste(' ',consumption)), hjust=0, size = 3) +
 coord_flip(clip = 'off', expand = TRUE) +
 scale_y_continuous(labels = scales::comma) +
 scale_x_reverse() +
 guides(color = FALSE, fill = FALSE) +
 theme_minimal() +
 theme(
   plot.title=element_text(size=20, hjust=0.5, face='bold', colour='grey', vjust=-1),
   plot.subtitle=element_text(size=10, hjust=0.5, face='italic', color='grey'),
   plot.caption =element_text(size=1, hjust=0.5, face='italic', color='grey'),
   axis.ticks.y = element_blank(),
   axis.text.y = element_blank(),
   plot.margin = margin(1,1,1,4, 'cm')
 )
plt<-static_plot + transition_states(states = year, transition_length = 4, state_length = 1) +
                   ease_aes('cubic-in-out') +
                   labs(title = 'Consumption in Year {closest_state}',
                        subtitle = 'Per Capita Consumption',
                        x = '',
                        y = 'Consumption')

plt #pritning our the moving graph

```

### Consumption Analysis:

First, we see Utah constantly at the bottom throughout all years. The top changes from New Hampshire, Montana, and North Dakota. These three top states are very interesting because they have been towards the bottom of the list on every other page and graphic except this one. One explanation is that these three states do not have very big populations so consumption is divided by a small capita making the measurement look larger. The second explanation is that all these states have a low lower tax per barrel cost therefore people from out of state might travel to purchase alcohol. Interviewing friends and family from the North East traveling to New Hampshire to buy alcohol common because they do not have sales tax. 5 states do not have sales tax as of 2019 [Alaska, Delaware, Montana, New Hampshire, and Oregon](https://taxfoundation.org/2020-sales-taxes/). This helps explain why New Hampshire and Montana are so high up on the list, not only do they have no sales tax but they also have small populations. According to the same source, California has the highest state-level sales tax which helps explain why it is so low on our rankings here but every other page so high up. 



---

## Brewery locations 

The below interactive map displays the location of all the breweries we have information on from the Beer API data source. This, of course, is not a complete list of all breweries but it is a nice selection that helps give a sense of where beer is produced in the United States. Scroll in and select a brewery to see more information! 

```{r brewer map, message = F, warning = F} 
#install.packages("leaflet")
library(leaflet)

pal <- colorNumeric(
  palette = "viridis",
  domain = beer$alcohol_by_volume)

beer %>%
  filter(alcohol_by_volume != 0) %>%
  mutate(
    click_label =
      str_c("<b>Brewer: ", name,
            "<br>ABV: ", alcohol_by_volume,
            "</b><br>City: ", city,
            "<br>State: ", state
            )
  ) %>%
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(~longitude, ~latitude,
                   #clusterOptions = markerClusterOptions(),
                   radius = 0.1,
                   color = ~pal(alcohol_by_volume),
                   popup = ~click_label)
```


### Brewery Map analysis 

We can see a concentration of breweries on the West Coast and in the North East! There are also some scattered breweries around middle America but the higher concentrations are around the edges closest to waterways. 


---



```{r cat_abv,collapse = T, message = F, warning = F, fig.width = 8, fig.height = 6, cache=TRUE}

# ## Alcohol by volume (ABV) pattern
# 
# **Alcohol by volume (ABV)** is defined to be the volume percent of alcohol (ethanol) contained in a given volume of an alcoholic beverage. 
# In our project, we are interested in exploring the pattern of ABV concerning the category/brewer/style of beer. 
# 
# ### By category
# 
# First, we looked at the pattern of ABV by beer's category. 
# 
# * It seems that **Belgian and French Ale** has the **highest** average ABV while the **North American Lager** has the **lowest** average AVB. 
# * The distribution of ABV of Belgian and French Ale is relatively bell-shaped while the other categories are skewed. 

# cat_abv = 
#   beer %>% 
#   replace_na(list(category = "NA", y = "unknown")) %>% 
#   group_by(category) %>% 
#   summarise(mean_abv = mean(alcohol_by_volume)) %>% 
#   arrange(desc(mean_abv)) 
# cat_abv
# cat_abv %>% 
#   mutate(category = fct_reorder(category, mean_abv)) %>% 
#   plot_ly(x = ~category, y = ~mean_abv, 
#           color = ~category, type = "bar", colors = "viridis") %>% 
#   layout(title = "Average ABV by Beer Category",
#          xaxis = list(title = "Beer Category",
#                       zeroline = TRUE),
#          yaxis = list(title = "Average ABV",
#                       range = c(0, 7)))
# 
# beer %>% 
#   mutate(category = fct_reorder(category, alcohol_by_volume)) %>% 
#   plot_ly(y = ~alcohol_by_volume, 
#           color = ~category, type = "box", colors = "viridis") %>% 
#   layout(title = "Boxplot of ABV by Beer Category",
#          xaxis = list(title = "Beer Category",
#                       zeroline = TRUE),
#          yaxis = list(title = "ABV",
#                       range = c(0, 21)))
```




```{r brewer_abv,collapse = T, message = F, warning = F, fig.width = 8, fig.height = 6, cache=TRUE}

# ### By brewer
# 
# Next, we looked at the pattern of ABV by beer's brewer. 
# 
# As there are 823 brewers listed in our dataset, we will show the **top 20** that has the highest average ABV, rather than all of them. 
# 
# * **Mendocino Brewing - Ukiah** has the highest average ABV. 
# * There are 424 brewers having average ABV value of 0. 




# brewer_abv = 
#   beer %>% 
#   group_by(brewer) %>% 
#   summarise(mean_abv = mean(alcohol_by_volume)) %>% 
#   arrange(desc(mean_abv))
# brewer_abv
# 
# #brewer_abv %>% filter(mean_abv == 0) #424
# 
# brewer_abv %>% 
#   slice(1:20) %>% 
#   mutate(brewer = fct_reorder(brewer, mean_abv)) %>%
#   plot_ly(x = ~brewer, y = ~mean_abv, 
#           color = ~brewer, type = "bar", colors = "viridis") %>%
#   layout(title = "Average ABV by Beer Brewer",
#          xaxis = list(title = "Beer Brewer",
#                       zeroline = TRUE),
#          yaxis = list(title = "Average ABV",
#                       range = c(8, 10.8)))
# 
# top_20_brewer = brewer_abv %>% slice(1:20) %>% select(brewer) %>% unlist()
# beer %>% 
#   filter(brewer %in% top_20_brewer) %>% 
#   mutate(brewer = fct_reorder(brewer, alcohol_by_volume)) %>% 
#   plot_ly(y = ~alcohol_by_volume, 
#           color = ~brewer, type = "box", colors = "viridis") %>% 
#   layout(title = "Boxplot of ABV by Beer Brewer",
#          xaxis = list(title = "ABV",
#                       zeroline = TRUE),
#          yaxis = list(title = "Average ABV"))
```



## Average Alcohol by volume by State 

Alcohol by volume (ABV) is defined to be the volume percent of alcohol (ethanol) contained in a given volume of an alcoholic beverage. In our project, we are interested in exploring the pattern of ABV in beer produced in each state. This average is considering all beer that does have alcohol content. Zero values were excluded because they represented non-alcoholic beer. The color of the state represents the state region. The data we are using is of course not a complete list of every single beer made in each state but rather a sample. 

```{r warning=FALSE, message=FALSE, cache=TRUE, fig.width = 8, fig.height = 6}
beer %>% 
  filter(alcohol_by_volume !=0 ) %>%
  group_by(state) %>% 
  filter(state %in% c(state.name) ) %>%
  summarize(
    mean_ABV = mean(alcohol_by_volume),
    CI_lower = mean(alcohol_by_volume, na.rm=TRUE) - 
      1.96 * sd(alcohol_by_volume, na.rm=TRUE)/sqrt(length(alcohol_by_volume)),
    CI_upper = mean(alcohol_by_volume, na.rm=TRUE) + 
      1.96 * sd(alcohol_by_volume, na.rm=TRUE)/sqrt(length(alcohol_by_volume))
  ) %>% 
  right_join(., region_name, by = "state") %>% # joining the regions in so we can color the graph
  mutate(
    state = fct_reorder(state, mean_ABV) # ordering the states according to mean_ABV
  )  %>%  # plotting!!
  drop_na(mean_ABV) %>%
  ggplot(aes(x = state, y = mean_ABV,color=state_region)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  #theme(legend.position = "none")  +
  labs(
    title = "Average ABV by State",
    subtitle = "National ABV in beer shown by dotten lines 5%-7% ",
    y = "ABV content",
    x = "State"
  ) +
  geom_hline(yintercept=5, linetype="dashed", 
                color = "black", size=1)+
  geom_hline(yintercept=7, linetype="dashed", 
                color = "black", size=1)
```

### Average ABV Analysis:
The State with the lowest ABI is Idaho and Utah. The state with the highest ABV is Delaware and Florida. In a common beer the average ABI according to the [National Consumers League](https://nclnet.org/alcohol_how_it_all_adds_up/#:~:text=One%20ounce%20of%20beer%20contains,5%20percent%20alcohol%20by%20volume) is 5-7%. From this graph, we see that 5 states have averages well below that range and 6 states have an average well above that range. Delaware’s 95% lower bound of its Confidence interval is well above 7%. 

---


## Common style by state

There are 62 styles listed in our dataset, and we will show the most common in each state displayed in the table. There are 8 different most common styles, each shown in a different shade. The count of how many beers are of that style in each state is shown by the count. Only 10 entries are showed per page so please click the next button to see more! 


```{r}
top_styles = beer %>% 
  filter(state %in% c(state.name)) %>%
  drop_na(style) %>%
  group_by(state) %>% 
  count(style) %>%
  slice(which.max(n)) %>%
  rename(
    count = n
  ) %>%
  relocate(style) 

top_styles %>%
 DT::datatable(., rownames = F, 
               options = list(pageLength = 10)) %>%
  DT::formatStyle(
      'style',
      #transform = 'rotateX(45deg) rotateY(20deg) rotateZ(30deg)',
      backgroundColor = DT::styleEqual(
        unique(top_styles$style), c(  "greenyellow", "steelblue", "lightyellow",   "lightblue", "paleturquoise",  "blueviolet", "slateblue","lightgreen")
        #c('lightsteelblue','lightcyan', 'lightblue', 'lightskyblue', 'cornflowerblue', 'skyblue', 'paleturquoise', 'powderblue' )
      )
  )

```


### Common style analysis:

It is extremely easy to sort each column by selecting the top column name. When selecting the style and seeing the styles arranged by alphabetical order it is easy to see that the most common type is the American-Style Pale Ale coming up as top in 17 states. Some of those states included California (count of 97), Washington (count of 33), and Illinois (count of 29). Style: American-Style Lager came up in 9 states and American-Style India Pale Ale also came up in 9 different states. 

Sorting by the counts the three top states are California (count of 97) with winning style American-Style Pale Ale, Wisconsin (count 77) winning style: American Style Lager, and Pennsylvania (count 37) winning style of American-style India Pale Ale. 


---

## ABI by our top 8 styles

Finally, we looked at the pattern of ABV by beer's style. There are 62 styles listed in our dataset, and we will show the **top 8** from the table above.  The colors are similar to the table. 

```{r style_abv,collapse = T, message = F, warning = F, fig.width = 8, fig.height = 6, cache=TRUE}
style_abv = 
  beer %>% 
  filter(style %in% c(unique(top_styles$style) )) %>%
  filter(alcohol_by_volume > 0) %>%
  group_by(style) %>% 
  summarise(mean_abv = mean(alcohol_by_volume, na.rm=TRUE)) %>% 
  arrange(desc(mean_abv))


style_abv %>% 
  #slice(1:20) %>% 
  mutate(style = fct_reorder(style, mean_abv)) %>% 
  plot_ly(x = ~style, y = ~mean_abv, 
          color = ~style, type = "bar", colors =  "viridis")  %>% # "viridis
  layout(title = "Average ABV by Top Beer Style",
         xaxis = list(title = "Beer Style",
                      zeroline = TRUE),
         yaxis = list(title = "Average ABV",
                      range = c(0, 10)))

```

### ABV by Style Analysis:
The style with the highest ABV is the Imperial or Double India Pale Ale. The next highest is the American-Style India Pale Ale. The lowest is the American-Style Lager. All the style are within our 5% to 7% range except for the Imperial or Double India Pale Ale which is well above 7%. 


