---
title: "read pdf data"
author: "Amy Pitts"
date: "11/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pdftools)
library(plyr)
library(tidyverse)
library(readxl)


library(plotly)
library(flexdashboard)
```

This data is gotten from [link](https://www.nbwa.org/resources/state-data). Specifically the pdf files at 
[Summary of Effective State Excise Tax Rates by State](https://www.nbwa.org/sites/default/files/Beer%20Excise%20Tax%202019%20-%20Revised%20July%202020.pdf)

[Shipments of Malt Beverages and Per Capita Consumption by State](https://www.nbwa.org/sites/default/files/2003%20and%202019%20State%20data%20Per%20Capita%20Sheets_1.pdf)



# read the data 
We then converted the pdf documents into excel documents using an online software. 
```{r messages = FALSE, warnings = FALSE }
state_df = read_excel("2003_and_2019_State_data_Per_Capita_perpage.xlsx",
                           sheet = 1, range = "A5:F56") %>%
                janitor::clean_names() %>%
                mutate(
                  year = rep(2003, 51)
                )

for( i in 2:17) {
  state_df = rbind(state_df, read_excel("2003_and_2019_State_data_Per_Capita_perpage.xlsx",
                             sheet = i, range = "A5:F56") %>%
                  janitor::clean_names() %>%
                  mutate(
                    year = rep(2002+i, 51)
                  )
             ) 
}

```


```{r message=TRUE, warning=FALSE}
state_tax_df = read_excel("Beer_Excise_Tax2019Revised_July_2020perpage.xlsx",
                           sheet = 1, range = "A5:G56") %>%
                janitor::clean_names() %>%
                mutate(
                  year = rep(2009, 51)
                )


for( i in 2:11) {
  state_tax_df = rbind(state_tax_df, read_excel("Beer_Excise_Tax2019Revised_July_2020perpage.xlsx",
                             sheet = i, range = "A5:G56") %>%
                  janitor::clean_names() %>%
                  mutate(
                    year = rep(2008+i, 51)
                  )
             ) 
}

```

###  Weighted average state excise tax rates based on published excise tax rates for package types, on/off
premise taxes, city/local taxes, and wholesale taxes. Estimates subject to change as new data become available. 



# VIZ looking at the state_tax_df

```{r}
state_tax_df %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~adjusted, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Effective Excise Tax (Volume Adjusted) (Tax per Barrel)")
```

```{r}
state_tax_df %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~rank_3, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Effective Excise Tax (Volume Adjusted) Rank ")
```



```{r}
state_tax_df %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~and_local_taxes, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Effective Excise Tax with Other and Local Taxes (Tax per Barrel)")
```


# VIZ looking at the state_df 
```{r}
state_df %>%
  filter(year > 2009) %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~shipments, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Shipments")
```

```{r}
state_df %>%
  filter(year > 2009) %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~rank_3, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Shipments rank")
```

```{r}
state_df %>%
  filter(year > 2009) %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~population, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "population above 21")
```

```{r}
state_df %>%
  filter(year > 2009) %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~consumption, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Consumption")
```

```{r}
state_df %>%
  filter(year > 2009) %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~rank_6, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Consumption Rank")
```


# look at the difference between state tax (those three columns)
```{r}
state_tax_df %>%
  select(state, adjusted, state_taxes, and_local_taxes, year) %>%
  mutate(
    diff_state_adj = state_taxes - adjusted,
    diff_local_adj = and_local_taxes - adjusted
  ) %>%
  filter(diff_state_adj > 0) %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~diff_state_adj, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Difference between state_taxes and adjusted")
```

```{r}
state_tax_df %>%
  select(state, adjusted, state_taxes, and_local_taxes, year) %>%
  mutate(
    diff_state_adj = state_taxes - adjusted,
    diff_local_adj = and_local_taxes - adjusted
  ) %>%
  filter(diff_local_adj > 0) %>%
  mutate(text_label = str_c("state: ", state)) %>% # creating text label 
  plot_ly( #using plotly to plot he tmax and tmin 
    x = ~year, y = ~diff_local_adj, color = ~factor(state), text = ~text_label,
    alpha = .5, type = "scatter", mode = "lines", colors = "viridis") %>%
  layout( # adding a title 
    title = "Difference between local_taxes and adjusted")
```

```{r}
# States that had different 
state_tax_df %>%
  select(state, adjusted, state_taxes, and_local_taxes, year) %>%
  mutate(
    diff_state_adj = state_taxes - adjusted,
    diff_local_adj = and_local_taxes - adjusted
  ) %>%
  filter(diff_state_adj > 0) %>%
  distinct(state ) 


state_tax_df %>%
  select(state, adjusted, state_taxes, and_local_taxes, year) %>%
  mutate(
    diff_state_adj = state_taxes - adjusted,
    diff_local_adj = and_local_taxes - adjusted
  ) %>%
  filter(diff_local_adj > 0) %>%
  distinct(state ) 
```




# you can ignore down here 
# First Pdf
First we are looking at the Summary of Effective State Excise Tax Rates by State. This is the loop that get data for all years 
```{r, message=FALSE, warning=FALSE}

# PDF <- pdf_text("Beer Excise Tax 2019 - Revised July 2020.pdf") %>%
#   readr::read_lines() #open the PDF inside your project folder
# 
# data_extract <- function(begin, end) {
#   PDF.small <-PDF[begin:end]  # remove lines
#   #PDF.tax
#   
#   df <- PDF.small %>%
#     str_squish() %>%
#     strsplit(split = " ") %>%# remove empty spaces
#     reduce(rbind) 
#   
#   data = tibble( 
#     "State" = df[,1], 
#      "Effective Excise Tax (Volume Adjusted)" = df[,2],
#      "Rank1" =df[,3], 
#      "Effective Excise Tax with Other State Taxes " = df[,4], 
#      "Rank2"= df[,5], 
#      "Effective Excise Tax with Other and Local Taxes " = df[,6],
#     "Rank3" = df[,7]
#     )
#   return(data)
# }
# df2009 = data_extract(6, 56)
# df2010 = data_extract(67, 118)
# df2011 = data_extract(128, 178)
# df2012 = data_extract(190,240) #2012
# df2013 = data_extract(252,302) #2013
# df2014 = data_extract(314,364) #2014
# df2015 = data_extract(376,426) #2015 #check ##########
# df2016 = data_extract(439,489) #2016
# df2017 = data_extract(502,552) #2017
# df2018 = data_extract(565,615) #2018
# df2019 = data_extract(628,678) #2019
```
Notice that every single tibble has problems with the state name. I can not figure out how to get the states that have two words as a name into just the state column. This will also mean we need to shift all the data in the column over one. This is going to be extremely annoying and I fix the problem above by just hard coding it but that shouldn't be our solution there should be another way.


# Second Pdf
This is the loop that get data for all years 
```{r, message=FALSE, warning=FALSE}
# PDF <- pdf_text("2003 and 2019 State data Per Capita Sheets_1.pdf") %>%
#   readr::read_lines() #open the PDF inside your project folder
# 
# data_extract <- function(begin, end) {
#   PDF.small <-PDF[begin:end]  # remove lines
#   #PDF.tax
#   
#   df <- PDF.small %>%
#     str_squish() %>%
#     strsplit(split = " ") %>%# remove empty spaces
#     reduce(rbind) 
#   
#   data = tibble( 
#     "State" = df[,1], 
#     "Shipments" = df[,2],
#     "Rank1" =df[,3], 
#     "Pop_21plus " = df[,4], 
#     "Per_Capita_Consumption"= df[,5], 
#     "Rank2" = df[,6]
#     )
#   return(data)
# }
# df2003_state = data_extract(6, 56)
# df2004_state = data_extract(65, 115)
# df2005_state = data_extract(124, 175)
# df2006_state = data_extract(183, 233) # 2006
# df2007_state = data_extract(242, 292) 
# df2008_state = data_extract(301, 351) # this will have a lot of 0
# df2009_state = data_extract(360, 410) # this will have a lot of 0 
# df2010_state = data_extract(419, 469) 
# df2011_state = data_extract(478, 528) 
# df2012_state = data_extract(537, 587) 
# df2013_state = data_extract(596, 646) 
# df2014_state = data_extract(655, 705) 
# df2015_state = data_extract(714, 764) 
# df2016_state = data_extract(773, 823) 
# df2017_state = data_extract(832, 882) 
# df2018_state = data_extract(891, 941) 
# df2019_state = data_extract(950, 1000) 
```



