---
title: "Beer Taxation Report in US"
author: 'Author: Amy Pitts (ajp2257), Ruiyang Li (rl3034), Wenbo Fei (wf2270), Ziyi Wang (zw2716)'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(rvest)
library(httr)
```

### To learn our project:
* A short [review](put screencast link here) of our project
* Explore more on our [website](https://iriswangziyi.github.io/p8105_final_project) 
* Find our Github [repository ](https://github.com/iriswangziyi/p8105_final_project)

### Motivation:
The US Government continues to control the consumption and production of Beer through regulations and taxes. The Alcohol and Tobacco Tax and Trade Bureau regulates people who engage in the alcohol beverage industry by requiring people to file an application before engaging in business (TTBGov - Beverage Alcohol, n.d.). For Breweries in particular they are required to file documents every year and the data is compiled into publicly available sources (TTBGov - Beer Statistics, n.d.). Through this reporting and taxation, the US profits enormously off of Beer. Since beer plays such an important role in the US economy it is important to analyze the publicly available government data all about taxation and production (TTBGov - Beverage Alcohol, n.d.). It is also equally interesting to look at the types of beer produced, location of breweries across the globe using an open-source API data set (Open Beer Database, n.d.). Our goal in this project is to get a better understanding of what kinds of beers are produced and how The US economy profits off of it.

Reference??

### Related work: 
Amy, do you want to include more in this section as we deleted some from the motivation last time?
(Anything that inspired you, such as a paper, a web site, or something we discussed in class.)

### Initial questions: 
* How much profit and product does each state in the US make each year?
* How does the tax rate change over time per state? Which state gives more beer tax? Any trends?
* What category/brewer/style of beer has the most Alcohol by volume (ABV)?
* Map location of each US brewer with interactive label showing category/style, size of marker showing ABV.

What questions are you trying to answer? How did these questions evolve over the course of the project? What new questions did you consider in the course of your analysis?
Discuss this in the meeting.

### Data: source, scraping method, cleaning
* Dataset 1

Yearly Statistical Beer Data by State (2008 – 2019) from [Alcohol and Tobacco Tax and Trade Bureau](https://www.ttb.gov/beer/statistics). This aggregated data contained records on Tax Determined, Taxable Volume of Bottles and Cans, Taxable Volume of Barrels and Kegs each year for each state in barrels.
```{r data1, warning=FALSE, message=F, cache=TRUE}
#install.packages("gdata")
site1 = "http://www.ttb.gov/images/pdfs/statistics/aggregated/aggr-data-beer_2008-2019.xlsx"

#Tax Determined (in Barrels)
tax_df  =  
  gdata::read.xls(site1, sheet = 1, header = T, skip = 6, nrow = 52) %>% #skip note
  janitor::clean_names() %>%
  select(1:13) %>%
  as_tibble() %>%
  rename_with( ~ sub("x", "", .x)) %>% # rename column names
  mutate(state = factor(state)) %>% #state as factor
  mutate_at(vars(2:13), ~ gsub(",", "", .x)) %>% #remove "," in tax values
  mutate_at(vars(2:13), as.numeric) # tax values as numeric

# Taxable Volume of Bottles and Cans* (in Barrels)
taxable_cans_df  = 
  gdata::read.xls(site1, sheet = 2, header = T, skip = 4, nrow = 52) %>% 
  janitor::clean_names() %>%
  select(1:13) %>%
  as_tibble() %>%
  rename_with( ~ sub("x", "", .x)) %>%
  mutate(state = factor(state)) %>%
  mutate_at(vars(2:13), ~ gsub(",", "", .x)) %>%
  mutate_at(vars(2:13), as.numeric)

# Taxable Volume of Barrels and Kegs*
taxable_barrels_df  = 
  gdata::read.xls(site1, sheet = 3, header = T, skip = 4, nrow = 52) %>% 
  janitor::clean_names() %>%
  select(1:13) %>%
  as_tibble() %>%
  rename_with( ~ sub("x", "", .x)) %>%
  mutate(state = factor(state)) %>%
  mutate_at(vars(2:13), ~ gsub(",", "", .x)) %>%
  mutate_at(vars(2:13), as.numeric)

head(tax_df)
head(taxable_cans_df)
head(taxable_barrels_df)
# write_csv(tax_df, "data_import_cleaning/tax.csv")
# write_csv(taxable_cans_df, "data_import_cleaning/tax_cans.csv")
# write_csv(taxable_barrels_df, "data_import_cleaning/tax_barrels_df.csv")
```


* Dataset 2

Open Beer database from [Opendatasoft](https://data.opendatasoft.com/explore/dataset/open-beer-database%40public-us/information/?rows=4588&timezone=&refine.country=United+States&location=2,16.98232,9.498&basemap=jawg.sunny&dataChart=eyJxdWVyaWVzIjpbeyJjb25maWciOnsiZGF0YXNldCI6Im9wZW4tYmVlci1kYXRhYmFzZUBwdWJsaWMtdXMiLCJvcHRpb25zIjp7fX0sImNoYXJ0cyI6W3siYWxpZ25Nb250aCI6dHJ1ZSwidHlwZSI6ImxpbmUiLCJmdW5jIjoiQVZHIiwieUF4aXMiOiJhYnYiLCJzY2llbnRpZmljRGlzcGxheSI6dHJ1ZSwiY29sb3IiOiIjMTQyRTdCIn1dLCJ4QXhpcyI6Imxhc3RfbW9kIiwibWF4cG9pbnRzIjoiIiwidGltZXNjYWxlIjoieWVhciIsInNvcnQiOiIifV0sImRpc3BsYXlMZWdlbmQiOnRydWUsImFsaWduTW9udGgiOnRydWV9). This dataset contains information of each beer product, including product name, universal product code, style, category, brewer along with its address and website, percentage of alcohol by volume, bitterness from hops in a beer, beer color, and description in text.

```{r read2, warning=FALSE, message=F, cache=TRUE}
beer_specific = 
  read_delim("https://public-us.opendatasoft.com/explore/dataset/open-beer-database/download/?format=csv&timezone=America/New_York&lang=en&use_labels_for_header=true&csv_separator=%3B", delim = ";") %>% # sep = ";"
  janitor::clean_names() %>%
  filter(country == "United States") %>% # only investigate beer in US
  separate(coordinates, c("latitude", "longitude"), sep = ",") # separate geographic info

head(beer_specific)
# write_csv(beer_specific, "data_import_cleaning/beer.csv")
```

* Dataset 3 -- Amy?
Amy, please add your data source, scraping method and cleaning, code and comment.

### Exploratory analysis: 
Visualizations, summaries, and exploratory statistical analyses. Justify the steps you took, and show any major changes to your ideas.
Each of us add our part, should include code that can generate the plot(please note file path), comment on the plots and answer the above corresponding initial questions part.
I will try to revise them in a reasonable order.

#### Amy:

#### Ruiyang:

**Alcohol by volume (ABV)** is defined to be the volume percent of alcohol (ethanol) contained in a given volume of an alcoholic beverage. In our project, we are interested in exploring the pattern of ABV concerning the category/brewer/style of beer (initial question 3). 

**By category**

First, we looked at the pattern of ABV by beer's category. 

* Based on our dataset, **Belgian and French Ale** has the **highest** average ABV while the **North American Lager** has the **lowest** average ABV. 

```{r cat_abv,collapse=TRUE,message=FALSE,warning=FALSE}
beer = read_csv("./data_import_cleaning/beer.csv")

cat_abv = 
  beer %>% 
  replace_na(list(category = "NA", y = "unknown")) %>% 
  group_by(category) %>% 
  summarise(mean_abv = mean(alcohol_by_volume)) %>% 
  arrange(desc(mean_abv)) 
cat_abv
cat_abv %>% 
  mutate(category = fct_reorder(category, mean_abv)) %>% 
  plot_ly(x = ~category, y = ~mean_abv, 
          color = ~category, type = "bar", colors = "viridis") %>% 
  layout(title = "Average ABV by Beer Category",
         xaxis = list(title = "Beer Category",
                      zeroline = TRUE),
         yaxis = list(title = "Average ABV",
                      range = c(0, 7)))
```

**By brewer**

Next, we looked at the pattern of ABV by beer's brewer. 

As there are 823 brewers listed in our dataset, we will show the **top 20** that has the highest average ABV, rather than all of them. 

* **Mendocino Brewing - Ukiah** has the highest average ABV. 
* There are 424 brewers having average ABV value of 0. 

```{r brewer_abv,collapse=TRUE,message=FALSE,warning=FALSE}
brewer_abv = 
  beer %>% 
  group_by(brewer) %>% 
  summarise(mean_abv = mean(alcohol_by_volume)) %>% 
  arrange(desc(mean_abv))
brewer_abv

#brewer_abv %>% filter(mean_abv == 0) #424

brewer_abv %>% 
  slice(1:20) %>% 
  mutate(brewer = fct_reorder(brewer, mean_abv)) %>%
  plot_ly(x = ~brewer, y = ~mean_abv, 
          color = ~brewer, type = "bar", colors = "viridis") %>%
  layout(title = "Average ABV by Beer Brewer",
         xaxis = list(title = "Beer Brewer",
                      zeroline = TRUE),
         yaxis = list(title = "Average ABV",
                      range = c(8, 10.8)))
```

**By style**

Finally, we looked at the pattern of ABV by beer's style. 

There are 62 styles listed in our dataset, and we will show the **top 20** that has the highest average ABV, as well as the **lowest 5**. 

* We can see that **Belgian-Style Quadrupel** has the higherst average ABV while both **Vienna-Style Lager** and **Specialty Honey Lager or Ale** has average ABV of 0. 

```{r style_abv,collapse=TRUE,message=FALSE,warning=FALSE}
style_abv = 
  beer %>% 
  group_by(style) %>% 
  summarise(mean_abv = mean(alcohol_by_volume)) %>% 
  arrange(desc(mean_abv))
style_abv

style_abv %>% 
  slice(1:20) %>% 
  mutate(style = fct_reorder(style, mean_abv)) %>% 
  plot_ly(x = ~style, y = ~mean_abv, 
          color = ~style, type = "bar", colors = "viridis")  %>%
  layout(title = "Average ABV by Beer Style",
         xaxis = list(title = "Beer Style",
                      zeroline = TRUE),
         yaxis = list(title = "Average ABV",
                      range = c(5.5, 12)))

tail(style_abv) %>% 
  rename(Style = style, `Average ABV` = mean_abv) %>% 
  slice(-1) %>% 
  mutate_at(2, round, 2) %>% 
  knitr::kable(caption = "Styles with Lowest 5 Average AVB") %>% 
  kableExtra::kable_styling(., bootstrap_options = c("striped", "hover"),
                            full_width = F)
```




#### Wenbo:

#### Iris:


### Additional analysis: Regression -- Ruiyang?
If you undertake formal statistical analyses, describe these in detail

[starts here]

We focus on two analyses in our project. One is to compare tax differences by jurisdiction group over time. The other is to model taxation under the regression analysis framework. More details can be found in the Analysis section on our website (link to be inserted here). 

**1. Preliminary Analysis** -- Tax differences by jurisdiction group

**Motivation**

Differing on the degree of control on liquor wholesales and retail, states can be categorized into two [types](https://www.ncsla.org/State-Officials.html) -- control jurisdiction and licensed jurisdiction, with licensed states having more control. Such categorization may lead to difference in taxation. Therefore, we are interested in examining if there is any difference in taxation by these two groups of states. 

**Procedures**

We performed t-test for each year from 2010 to 2019 and would like to see if there is any significant difference in the cumulative tax between control states and licensed states. 

**Findings**

Based on the test results, however, we did not find sufficient evidence showing any significant difference between two jurisdiction groups in both the cumulative tax collected and the tax per barrel from 2010 to 2019. 

We speculated that there may be some confounding variables that could potentially affect the relationship between taxation and the jurisdiction group. Therefore, we decided to further perform regression analysis. Specifically, we would like to explore more regarding the relationship between taxation and jurisdiction group, year, shipments, population, and consumption.

**2. Regression Analysis**

**Variables of interest**

Our explaining variables of interest include jurisdiction group, year, shipments, population, and consumption. Their detailed explanation are as below.

* group: jurisdiction group (control vs licensed)
* shipments: amount of barrels shipped
* population: the number of individuals who are 21 years old or older
* consumption: consumption of barrels per capital

**Model**

Our intended model is 

$$Tax = \beta_0 + \beta_1 \ Group + \beta_2 Year + \beta_3 \ Shipments + \beta_4 \ Population+ \beta_5 \ Consumption$$

We looked at both the cumulative tax collected and the tax per barrel. 

**Results & Findings**

In the model of the **tax per barrel**, all the variables are **not significant** at the 5% significance level; further the model is poorly fitted as the adjusted $R^2$ is approximately 0. Therefore, we will mostly focus on the cumulative tax collected. 

In the model of **cumulative tax collected**, we found that: 

* All variables in our model are **significant** at the 5% significance level. 
* Our model fit is acceptable with an adjusted $R^2 = 0.51$. 
* Previously, we did not find any significant difference in the cumulative tax between two jurisdiction groups. However, after controlling for year, shipments, population and consumption, we found that **licensed states** are estimated to have approximately **7.5k less cumulative tax collected** than the control states.
* **Cumulative tax collected** is estimate to **increase approximately 7k per year**, holding the group, shipments, population and consumption unchanged. 
* Cumulative tax collected is estimated to **increase approximately 1k for one unit increase in consumption per capital**, holding the group, year, shipments, and population unchanged. 
* Population and shipments have estimated coefficients close to 0, though they have significant p-values. 

[ends here]



### Discussion: 
What were your findings? Are they what you expect? What insights into the data can you make?

Discuss in the meeting.

### Resources:
* Open Beer Database. (n.d.). Retrieved November 6, 2020, from https://data.opendatasoft.com/explore/dataset/open-beer-database@public-us/table/
* TTBGov—Beer Statistics. (n.d.). Retrieved November 6, 2020, from https://www.ttb.gov/beer/statistics
* TTBGov—Beverage Alcohol. (n.d.). Retrieved November 6, 2020, from https://www.ttb.gov/alcohol/beverage-alcohol