---
title: "Proposal_DataSource"
author: "Wenbo Fei"
date: "11/3/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
```

# Data 1 Tax data of beer
Yearly Statistical Beer Data by State (2008 – 2019) from 
[Alcohol and Tobacco Tax and Trade Bureau](https://www.ttb.gov/beer/statistics). This aggregated data contained records on Tax Determined, Taxable Volume of Bottles and Cans, Taxable Volume of Barrels and Kegs each year for each state in barrels.

```{r read1}
#install.packages("gdata")
site1 = "http://www.ttb.gov/images/pdfs/statistics/aggregated/aggr-data-beer_2008-2019.xlsx"

#Tax Determined (in Barrels)
tax_df  =  
  gdata::read.xls(site1, sheet = 1, header = T, skip = 6, nrow = 52) %>% 
  janitor::clean_names() %>%
  select(1:13) %>%
  as_tibble() %>%
  rename_with( ~ sub("x", "", .x)) %>% # rename column names
  mutate(state = factor(state)) %>% #state as factor
  mutate_at(vars(2:13), ~ gsub(",", "", .x)) %>% #remove , in tax values
  mutate_at(vars(2:13), as.numeric) # tax values as numeric

# Taxable Volume of Bottles and Cans* (in Barrels)
taxable_cans_df  = 
  gdata::read.xls(site1, sheet = 2, header = T, skip = 4, nrow = 52) %>% 
  janitor::clean_names() %>%
  select(1:13) %>%
  as_tibble() %>%
  rename_with( ~ sub("x", "", .x)) %>%
  mutate(state = factor(state)) %>%
  mutate_at(vars(2:13), ~ gsub(",", "", .x)) %>%
  mutate_at(vars(2:13), as.numeric)

# Taxable Volume of Barrels and Kegs*
taxable_barrels_df  = 
  gdata::read.xls(site1, sheet = 3, header = T, skip = 4, nrow = 52) %>% 
  janitor::clean_names() %>%
  select(1:13) %>%
  as_tibble() %>%
  rename_with( ~ sub("x", "", .x)) %>%
  mutate(state = factor(state)) %>%
  mutate_at(vars(2:13), ~ gsub(",", "", .x)) %>%
  mutate_at(vars(2:13), as.numeric)


# View(tax_df)
# View(taxable_cans_df)
# View(taxable_barrels_df)
# write_csv(tax_df, "tax.csv")
# write_csv(taxable_cans_df, "tax_cans.csv")
#write_csv(taxable_barrels_df, "tax_barrels_df.csv")
```

## Data 2: Beer Product Information
Open Beer database from [Opendatasoft](https://data.opendatasoft.com/explore/dataset/open-beer-database%40public-us/information/?rows=4588&timezone=&refine.country=United+States&location=2,16.98232,9.498&basemap=jawg.sunny&dataChart=eyJxdWVyaWVzIjpbeyJjb25maWciOnsiZGF0YXNldCI6Im9wZW4tYmVlci1kYXRhYmFzZUBwdWJsaWMtdXMiLCJvcHRpb25zIjp7fX0sImNoYXJ0cyI6W3siYWxpZ25Nb250aCI6dHJ1ZSwidHlwZSI6ImxpbmUiLCJmdW5jIjoiQVZHIiwieUF4aXMiOiJhYnYiLCJzY2llbnRpZmljRGlzcGxheSI6dHJ1ZSwiY29sb3IiOiIjMTQyRTdCIn1dLCJ4QXhpcyI6Imxhc3RfbW9kIiwibWF4cG9pbnRzIjoiIiwidGltZXNjYWxlIjoieWVhciIsInNvcnQiOiIifV0sImRpc3BsYXlMZWdlbmQiOnRydWUsImFsaWduTW9udGgiOnRydWV9). This dataset contains information of each beer product, including product name, universal product code, style, category, brewer along with its address and website, percentage of alcohol by volume, bitterness from hops in a beer, beer color, and description in text.
```{r read2}
beer_specific = 
  read_delim("https://public-us.opendatasoft.com/explore/dataset/open-beer-database/download/?format=csv&timezone=America/New_York&lang=en&use_labels_for_header=true&csv_separator=%3B", delim = ";") %>%
  janitor::clean_names() %>%
  filter(country == "United States") %>%
  separate(coordinates, c("latitude", "longitude"), sep = ",")

# View(beer_specific)
# write_csv(beer_specific, "beer.csv")
```

* This dataset seems to have many missing values while the website didn't give any explanation. Some of them don't have a description, many of them share a product code 0.